### 2021-05-27 geography/ia/paper.tex
geo ia work -> toward final draft

Our results for the bipolar survey are shown in Appendix \ref{app:bipolar}

When tallied, the total scores for each site can be expressed as a fraction over 84, as shown in Figures 4, 5.

When plotted on a map, these totals can be shown with a gradient of colors.

\begin{figure}[H]
    \centering
    \includegraphics[width=0.7\linewidth]{media/7eColors.png}
    \caption{Each site in the VVI\textsuperscript{th}, with its respective total score expressed as a percentage for clarity, and a color assigned based on the gradient in Figure 8.}
\end{figure}

\begin{figure}[H]
    \centering
    \includegraphics[width=0.7\linewidth]{media/16eColors.png}
    \caption{Each site in the XVI\textsuperscript{th}, with a percentage. Color assigned with gradient in Figure 8.}
\end{figure}

@@

In order to either support or disprove our third hypothesis, it is important to study how trees are scattered in Paris, which reveals how dispersed green spaces are from one another. A statistical test called the Nearest Neighbor Index (NNI) test can provide a reasonable answer to this: if the index is similar for both sites, it can easily be said then that our hypothesis is supported. This value also reveals information about the distribution of trees: clustered, random or in a regular pattern, as seen in Figure 5 below. These values will be analysed in the later section \ref{sec:analysis} Analysis.

@@

@@

Once our data collected, we can analyse certain patterns that appear

\subsection{Data collected}

>>>>

@@

In order to either support or disprove our third hypothesis, it is important to study how trees are scattered in Paris, which reveals how dispersed green spaces are from one another. A statistical test called the Nearest Neighbor Index (NNI) test can provide a reasonable answer to this: if the index is similar for both sites, it can easily be said then that our hypothesis is supported. This value also reveals information about the distribution of trees: clustered, random or in a regular pattern, as seen in Figure 4 below. These values will be presented and analysed in the later section \ref{sec:analysis}. Data \& Analysis.

@@

\subsubsection{Questionnaire}

We also collected data from a questionnaire sent out to many people. This questionnaire contained the two questions \textit{"Do you believe that the Passy area has more green spaces than the area around the Eiffel tower? (Not including the champ de mars)"} and \textit{"How much litter is in the Passy area compared to around the Eiffel tower?"}. The data collected from this survey is listed in Section \ref{sec:data}. We surveyed our year, which has people that live in and frequent these two areas.

@@

Once our data collected, we can analyse certain patterns or appearances that do not follow a general trend. Our data is shown below in Subsection \ref{sec:data}.

\subsection{Data collected}
\label{sec:data}

Our results for the bipolar survey are shown in Appendix \ref{app:bipolar} (not shown here due to large size). When tallied, the total scores for each site can be expressed as a fraction over 84, as shown in Figures 5, 6.

When plotted on a map, these totals can be shown as percentages ($\frac{s}{84} \cdot 100$, where $s$ is the total score) with a gradient of colors, as seen below in Figures 7, 8:

\begin{figure}[H]
    \centering
    \includegraphics[width=0.7\linewidth]{media/7eColors.png}
    \caption{Each site in the VVI\textsuperscript{th}, with its respective total score expressed as a percentage for clarity, and a color assigned based on the gradient in Figure 9.}
\end{figure}

\begin{figure}[H]
    \centering
    \includegraphics[width=0.7\linewidth]{media/16eColors.png}
    \caption{Each site in the XVI\textsuperscript{th}, with a percentage. Color assigned with gradient in Figure 9.}
\end{figure}

As for images collected during our inspections of the sites, for the sake of keeping the file size of this paper down, I will not attach the images collected and they will be available for download or viewing at the URL \url{https://github.com/kinnounko/notes/tree/main/geography/ia}.

The dataset collected from the questionnaire is shown in the tables in Figures 10, 11.

\begin{figure}[H]
    \begin{center}
        \begin{tabular}{||c c||}
            \hline
            Answer             & Number of people that agree \\ [0.5ex]
            \hline\hline
            Significantly Less & 4                           \\
            \hline
            Less               & 8                           \\
            \hline
            About the same     & 8                           \\
            \hline
            More               & 10                          \\
            \hline
            Significantly more & 0                           \\ [1ex]
            \hline
        \end{tabular}
    \end{center}
    \caption{\textit{Do you believe that the Passy area has more green spaces than the area around the Eiffel tower? (Not including the champ de mars)}}
\end{figure}

\begin{figure}[H]
    \begin{center}
        \begin{tabular}{||c c||}
            \hline
            Answer             & Number of people that agree \\ [0.5ex]
            \hline\hline
            Significantly Less & 3                           \\
            \hline
            Less               & 10                           \\
            \hline
            About the same     & 12                           \\
            \hline
            More               & 5                          \\
            \hline
            Significantly more & 0                           \\ [1ex]
            \hline
        \end{tabular}
    \end{center}
    \caption{\textit{How much litter is in the Passy area compared to around the Eiffel tower?}}
\end{figure}
